Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2025-01-20 paper/paper.tex
minor

Auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}. Different tools have been developed to check the fairness of AI models\cite{saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}. We use a tool produced from our previous work\cite{yuan2024ensuring}.

@@

In the framework of our previous work\cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits. However, this practice raises both security and privacy concerns.

@@

We employed the tools of the winner of the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.

>>>>

Auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}. Different tools have been developed to check the fairness of AI models\cite{saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}. We use a tool produced from \cite{yuan2024ensuring}.

@@

In the framework of \cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits. However, this practice raises both security and privacy concerns.

@@

We employed the tools of the winner of the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from \cite{yuan2024ensuring}.
